Cover Letter: Cudele (Paper 306)

### 2018-01-08 paper/sections/6_results.tex
paper: typos
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

Cudele lets \oldcomment{users}\newcomment{administrators} construct
consistency/durability guarantees using well-established research techniques
from other systems; so instead of evaluating the scalability and performance of
the techniques themselves against other file systems, we show that (1) the
mechanisms we propose are useful for constructing semantics used by real
systems, (2) the techniques can work side-by-side in the same
namespace\oldcomment{, and (3) the combination of these techniques can help the
system scale further when subtrees are coupled to the correct type of
application}. \newcomment{These techniques have already proven to be effective
and scalable in systems that specialize an entire namespace according to a
single optimization strategy ({\it e.g.}, Lustre, BatchFS, DeltaFS), so our
evaluation explores the behavior of the consistency/durability mechanisms and
their effect with and without isolation.}

@@

\oldcomment{Figure~\ref{fig:composable-mechanisms} shows the runtime of the
Cudele mechanisms for a single client creating files in the same directory, }
\newcomment{We measure the overhead of each Cudele mechanism by having 1 client create
100K files in a directory for various subtree configurations.
Figure~\ref{fig:composable-mechanisms} shows the time that it takes each Cudele
mechanism to process all metadata events.  Results are} normalized to the time
it takes to write \oldcomment{100K file create} updates to the client's in-memory journal
({\it i.e.} the Append Client Journal mechanism).  \newcomment{The first graph
groups the consistency mechanisms, the second groups the durability mechanisms,
and the third has compositions representing real-world systems.} \oldcomment{Stream is an
approximation of the overhead and is calculated by subtracting the runtime of
the job with the journal turned off from the runtime with the journal turned
on.  100K is the maximum recommended size of a directory in CephFS;
preliminary experiments with larger directory sizes show memory problems.}

@@

% RPCs vs. apply: calls to metadata server vs. RADOS TODO: why is apply so
% slow.  apply: no CephFS changes, pulls/pushes same RADOS obj.  v_apply vs.
% apply/persist: communicating through RADOS
{\it Overhead of \oldcomment{RPCs}\newcomment{Consistency}:} RPCs is
\oldcomment{\(66\times\)}\newcomment{\(19.9\times\)} slower than Volatile Apply
because sending individual metadata updates over the network is costly.  While
RPCs sends a request for every file create, Volatile Apply \oldcomment{writes
all the updates to the in-memory journal and applies them}\newcomment{writes
directly} to the in-memory data structures in the metadata server. While
communicating the decoupled namespace directly to the metadata server
\newcomment{with Volatile Apply} is faster, communicating through the object
store \newcomment{with Nonvolatile Apply} is
\oldcomment{\(10\times\)}\newcomment{\(78\times\)} slower.  \oldcomment{{\it
Overhead of Nonvolatile Apply:} The cost of Nonvolatile Apply is much larger
than all the other mechanisms.  That mechanism}\newcomment{Nonvolatile Apply}
was not implemented as part of Cudele -- it was a debugging and recovery tool
packaged with CephFS. It works by iterating over the updates in the journal and
pulling all objects that {\it may} be affected by the update.  This means that
two objects are repeatedly pulled, updated, and pushed: the object that houses
the experiment directory and the object that contains the root directory ({\it
i.e.}, \texttt{/}).  \oldcomment{The cost of communicating through the object
store is shown by comparing the runtime of Volatile Apply + Global Persist to
Nonvolatile Apply.  These two operations} \newcomment{Nonvolatile Apply
(\(78\times\)) and composing Volatile Apply + Global Persist (\(1.3\times\))}
end up with the same final metadata state but using Nonvolatile Apply is
clearly inferior.

% persist vs. save: one disk vs. many
{\it Parallelism of the Object Store:}
\newcomment{Stream, which is an approximation (journal on minus journal off) has
the highest slowdown at \(2.4\times\) because the overhead of maintaining and
streaming the journal is incurred by the metadata server}.  Comparing Local and
Global Persist demonstrates the bandwidth advantages of storing the journal in
a distributed object store. The Global Persist performance is \newcomment{only
\(0.2\times\) slower than Local Persist because Global
Persist}\oldcomment{\(1.5\times\) faster because the object store} is
leveraging the collective bandwidth of the disks in the cluster. This benefit
comes from the object store itself but should be acknowledged when making
decisions for the application; the bandwidth of the object store can help
mitigate the overheads of globally persisting metadata updates. The storage per
journal update is about 2.5KB. So the storage footprint scales linearly with
the number of metadata creates and suggests that updates for a million updates
in a single journal would be \newcomment{2.38GB}\oldcomment{2.5KB \(*\) 1
million files \(=\) 2.38GB.  Transfer times for payloads of this size in most
HPC/data center networks are reasonable.}

@@

\newcomment{{\it Composing Mechanisms}: The graph on the right of
Figure~\ref{fig:composable-mechanisms} shows how applications can compose
mechanisms together to get the consistency/durability guarantees they need in a
global namespace.  We label the \(x\)-axis with systems that employ these
semantics, as described in Figure~\ref{fig:subtree-policies}.  We make no
guarantees during execution of the mechanisms or when transitioning semantics
-- the semantics are guaranteed {\it once the mechanism completes}.  So if
servers fail during a mechanism, metadata or data may be lost. This graph shows
how we can build application-specific subtrees by composing mechanisms and that
coupling well-established techniques to specific applications results in a more
scalable global namespace.}

@@

\oldcomment{Next we show how we can build application-specific subtrees by
composing mechanisms and that this approach of coupling well-established
techniques to specific applications results in a more a scalable global
namespace.} We start with clients creating files in private directories because
this workload is heavily studied in HPC~\cite{weil:sc2004-dyn-metadata,
ren:sc2014-indexfs, patil:fast2011-giga, zheng:pdsw2014-batchfs,
sevilla:sc15-mantle}, mostly due to checkpoint-restart~\cite{bent_plfs_2009}.
A more familiar example is uncompressing an archive ({\it e.g.}, \texttt{tar
xzf}), where the file system services a flash crowd of creates across all
directories as shown in Figure~\ref{fig:overhead-creates}.  But the workload
also appears in cloud workloads: Hadoop/Spark use the file \newcomment{system
to assign work units to workers and the performance is proportional to the
open/create throughput of the underlying file system~\cite{xiao:socc15-shardfs,
shi:vldb15-spark, shvachko:login2012-hdfs-scalability}; Spark queries have an
O(\(n\)) complexity, where \(n\) is the number of partitions.  Big Data
Benchmark jobs examined in~\cite{chaimov:hpdc16-spark} have on the order of
15,000 file opens or creates just to start a single Spark query and the Lustre
system they tested on did not handle creates well, showing up to a \(24\times\)
slowdown compared to other metadata operations. Common approaches to solve
these types of bottlenecks is to change the application behavior or to design a
new file system, like BatchFS or DeltaFS, that uses one set of metadata
optimizations for the entire namespace.} \oldcomment{ abstraction to exchange
work units to workers or to indicate when jobs complete  The workload is
clients creating 100K files in private directories in the same global
namespace.}

@@

\newcomment{\textbf{Cudele setup}: enable global durability with Stream and
strong consistency with RPCs to mirror the setup from the problem presented in
Figure~\ref{fig:overhead-b}. We configure one subtree with an interfere policy
of ``allow" and another with subtree with ``block" so \texttt{-EBUSY} is
returned to interfering clients.  The former is the default behavior in file
systems and the latter isolates performance from malicious clients.}

\oldcomment{We only scale to 15 clients because the performance variability of
a nearly overloaded metadata server, in our case 18 clients, is too high.}
Figure~\ref{fig:block-allow} plots the overhead of the slowest
client\oldcomment{and the error bars are the standard deviation of 3 runs.
``Interfere (Fig 3c)" is the result from Figure~\ref{fig:overhead-b};
``Interfere" uses the allow/block API to return \texttt{-EBUSY} to interfering
clients; and ``Isolated" is the baseline performance without an interfering.
Each subtree has RPCs and Stream enabled.  Results are normalized to the
runtime of a single client creating files in a directory.  Note that IndexFS
has a similar behavior to ``interfere" with leases, except clients block.
}\newcomment{, normalized to 1 client that creates 100K files in isolation
(about 513 creates/sec). ``Interference" and ``no interference" is the
performance with and without an interfering client touching files in every
directory, respectively. The goal is to explicitly isolate clients so that
performance is similar to the ``no interfere" curve, which has lower slowdowns
(on average, \(1.42\times\) per client compared to \(1.67\times\) per client
for ``interfere") and less variability (on average, a standard deviation of
0.06 compared to 0.44 for ``interfere").  ``Block interference" uses the Cudele
API to block interfering clients and the slowdown (\(1.34\times\) per client)
and variability (0.09) look very similar to ``no interfere" for larger
clusters. For smaller clusters the overhead to reject requests is more evident
when the metadata server is underloaded so the slowdowns are similar to
``interfere".  Clients can block interfering clients to get the same
performance as isolated clients but there is a non-negligible overhead for
rejecting requests when the metadata server is not operating at peak
efficiency.}

@@

The final use case shows how the API gives
\oldcomment{users}\newcomment{administrators} fine-grained control of the
consistency semantics \newcomment{to support current practices and experimental
workflows}. \oldcomment{The use case is that u}\newcomment{U}sers often
leverage the file system to check the progress of jobs using \texttt{ls} even
though this operation is notoriously heavy-weight~\cite{carns:ipdps09-pvfs,
eshel:fast10-panache}. The number of files or size of the files is indicative
of the progress. This practice is not too different from systems that use the
file system to manage the progress of jobs; Spark and Hadoop write to temporary
files, renames them when complete, and creates a ``DONE" file to indicate to
the runtime that the task did not fail and should not be re-scheduled on
another node. \newcomment{Also, the browser interface lets Hadoop/Spark users check the
progress by querying the file system and returning a \% of job complete
metric.}

@@

As expected, syncing namespace updates too frequently has the highest overhead
(up to 9\% overhead if done every second). The optimal sync interval for
performance is 10 seconds, which only incurs 2\% overhead), because larger
intervals must write more updates to disk and network. For the 25 second
interval, the client only pauses 3-4 times but each sync writes about 278
thousand updates at once, which is a journal of size 678MB.

>>>>

Cudele lets \oldcomment{users}\newcomment{administrators} construct
consistency/durability guarantees using well-established research techniques
from other systems; so instead of evaluating the scalability and performance of
the techniques themselves against other file systems, we show that (1) the
mechanisms we propose are useful for constructing semantics used by real
systems and (2) the techniques can work side-by-side in the same
namespace for common use cases\oldcomment{, and (3) the combination of these techniques can help the
system scale further when subtrees are coupled to the correct type of
application}. \newcomment{These techniques have already proven to be effective
and scalable in systems that specialize an entire namespace according to a
single optimization strategy ({\it e.g.}, Lustre, BatchFS, DeltaFS).}
%, so our
%evaluation explores the behavior of the consistency/durability mechanisms and
%their effect with and without isolation.}

@@

\oldcomment{Figure~\ref{fig:composable-mechanisms} shows the runtime of the
Cudele mechanisms for a single client creating files in the same directory, }
\newcomment{We measure the overhead of each Cudele mechanism by having 1 client create
100K files in a directory for various subtree configurations.
Figure~\ref{fig:composable-mechanisms} shows the time that it takes each Cudele
mechanism to process all metadata events.  Results are} normalized to the time
it takes to write \oldcomment{100K file create} updates to the client's in-memory journal
({\it i.e.} the Append Client Journal mechanism), which is about 11K creates/sec.  \newcomment{The first graph
groups the consistency mechanisms, the second groups the durability mechanisms,
and the third has compositions representing real-world systems.} \oldcomment{Stream is an
approximation of the overhead and is calculated by subtracting the runtime of
the job with the journal turned off from the runtime with the journal turned
on.  100K is the maximum recommended size of a directory in CephFS;
preliminary experiments with larger directory sizes show memory problems.}

@@

% RPCs vs. apply: calls to metadata server vs. RADOS TODO: why is apply so
% slow.  apply: no CephFS changes, pulls/pushes same RADOS obj.  v_apply vs.
% apply/persist: communicating through RADOS
{\it Overhead of \oldcomment{RPCs}\newcomment{Consistency}:} RPCs is
\oldcomment{\(66\times\)}\newcomment{\(19.9\times\)} slower than Volatile Apply
because sending individual metadata updates over the network is costly.  While
RPCs sends a request for every file create, Volatile Apply \oldcomment{writes
all the updates to the in-memory journal and applies them}\newcomment{writes
directly} to the in-memory data structures in the metadata server. While
communicating the decoupled namespace directly to the metadata server
\newcomment{with Volatile Apply} is faster, communicating through the object
store \newcomment{with Nonvolatile Apply} is
\oldcomment{\(10\times\)}\newcomment{\(78\times\)} slower.  \oldcomment{{\it
Overhead of Nonvolatile Apply:} The cost of Nonvolatile Apply is much larger
than all the other mechanisms.  That mechanism}\newcomment{Nonvolatile Apply}
was not implemented as part of Cudele -- it was a debugging and recovery tool
packaged with CephFS. It works by iterating over the updates in the journal and
pulling all objects that {\it may} be affected by the update.  This means that
two objects are repeatedly pulled, updated, and pushed: the object that houses
the experiment directory and the object that contains the root directory ({\it
i.e.} \texttt{/}).  \oldcomment{The cost of communicating through the object
store is shown by comparing the runtime of Volatile Apply + Global Persist to
Nonvolatile Apply.  These two operations} \newcomment{Nonvolatile Apply
(\(78\times\)) and composing Volatile Apply + Global Persist (\(1.3\times\))}
end up with the same final metadata state but using Nonvolatile Apply is
clearly inferior.

% persist vs. save: one disk vs. many
{\it Parallelism of the Object Store:}
\newcomment{Stream, which is an approximation (journal on minus journal off), has
the highest slowdown at \(2.4\times\) because the overhead of maintaining and
streaming the journal is incurred by the metadata server}.  Comparing Local and
Global Persist demonstrates the bandwidth advantages of storing the journal in
a distributed object store. The Global Persist performance is \newcomment{only
\(0.2\times\) slower than Local Persist because Global
Persist}\oldcomment{\(1.5\times\) faster because the object store} is
leveraging the collective bandwidth of the disks in the cluster. This benefit
comes from the object store itself but should be acknowledged when making
decisions for the application; the bandwidth of the object store can help
mitigate the overheads of globally persisting metadata updates. The storage per
journal update is about 2.5KB. So the storage footprint scales linearly with
the number of metadata creates and suggests that updates for a million updates
in a single journal would be \newcomment{2.38GB}\oldcomment{2.5KB \(*\) 1
million files \(=\) 2.38GB.  Transfer times for payloads of this size in most
HPC/data center networks are reasonable.}

@@

\newcomment{{\it Composing Mechanisms}: The graph on the right of
Figure~\ref{fig:composable-mechanisms} shows how applications can compose
mechanisms together to get the consistency/durability guarantees they need in a
global namespace.  We label the \(x\)-axis with systems that employ these
semantics, as described in Figure~\ref{fig:subtree-policies}.  We make no
guarantees during execution of the mechanisms or when transitioning semantics
-- the semantics are guaranteed {\it once the mechanism completes}.  So if
servers fail during a mechanism, metadata or data may be lost. This graph shows
how we can build application-specific subtrees by composing mechanisms and the performance of
coupling well-established techniques to specific applications over the same file system.}

%results in a more
%scalable global namespace.}

@@

\oldcomment{Next we show how we can build application-specific subtrees by
composing mechanisms and that this approach of coupling well-established
techniques to specific applications results in a more a scalable global
namespace.} We start with clients creating files in private directories because
this workload is heavily studied in HPC~\cite{weil:sc2004-dyn-metadata,
ren:sc2014-indexfs, patil:fast2011-giga, zheng:pdsw2014-batchfs,
sevilla:sc15-mantle}, mostly due to checkpoint-restart~\cite{bent_plfs_2009}.
A more familiar example is uncompressing an archive ({\it e.g.}, \texttt{tar
xzf}), where the file system services a flash crowd of creates across all
directories as shown in Figure~\ref{fig:overhead-creates}.  But the workload
also appears in cloud workloads: Hadoop/Spark use the file \newcomment{system
to assign work units to workers and the performance is proportional to the
open/create throughput of the underlying file system~\cite{xiao:socc15-shardfs,
shi:vldb15-spark, shvachko:login2012-hdfs-scalability}; Big Data Benchmark jobs
examined in~\cite{chaimov:hpdc16-spark} have on the order of 15,000 file opens
or creates just to start a single Spark query and the Lustre system they tested
on did not handle creates well, showing up to a \(24\times\) slowdown compared
to other metadata operations. Common approaches to solve these types of
bottlenecks is to change the application behavior or to design a new file
system, like BatchFS or DeltaFS, that uses one set of metadata optimizations
for the entire namespace.} \oldcomment{ abstraction to exchange work units to
workers or to indicate when jobs complete  The workload is clients creating
100K files in private directories in the same global namespace.}

@@

\newcomment{\textbf{Cudele setup}: enable global durability with Stream and
strong consistency with RPCs to mirror the setup from the problem presented in
Figure~\ref{fig:overhead-b}. We configure one subtree with an interfere policy
of ``allow" and another subtree with ``block" so \texttt{-EBUSY} is
returned to interfering clients.  The former is the default behavior in file
systems and the latter isolates performance from malicious clients.}

\oldcomment{We only scale to 15 clients because the performance variability of
a nearly overloaded metadata server, in our case 18 clients, is too high.}
Figure~\ref{fig:block-allow} plots the overhead of the slowest
client\oldcomment{and the error bars are the standard deviation of 3 runs.
``Interfere (Fig 3c)" is the result from Figure~\ref{fig:overhead-b};
``Interfere" uses the allow/block API to return \texttt{-EBUSY} to interfering
clients; and ``Isolated" is the baseline performance without an interfering.
Each subtree has RPCs and Stream enabled.  Results are normalized to the
runtime of a single client creating files in a directory.  Note that IndexFS
has a similar behavior to ``interfere" with leases, except clients block.
}\newcomment{, normalized to 1 client that creates 100K files in isolation
(about 513 creates/sec). ``Interference" and ``no interference" is the
performance with and without an interfering client touching files in every
directory, respectively. The goal is to explicitly isolate clients so that
performance is similar to the ``no interference" curve, which has lower
slowdowns (on average, \(1.42\times\) per client compared to \(1.67\times\) per
client for ``interfere") and less variability (on average, a standard deviation
of 0.06 compared to 0.44 for ``interfere").  ``Block interference" uses the
Cudele API to block interfering clients and the slowdown (\(1.34\times\) per
client) and variability (0.09) look very similar to ``no interference" for a
larger number of clients. For smaller clusters the overhead to reject requests
is more evident when the metadata server is underloaded so the slowdowns are
similar to ``interference".  We conclude that administrators can block interfering clients to get the same
performance as isolated scenarios but there is a non-negligible overhead for
rejecting requests when the metadata server is not operating at peak
efficiency.}

@@

The final use case shows how the API gives
\oldcomment{users}\newcomment{administrators} fine-grained control of the
consistency semantics \newcomment{to support current practices and scientific
workflows in HPC}. \oldcomment{The use case is that u}\newcomment{U}sers often
leverage the file system to check the progress of jobs using \texttt{ls} even
though this operation is notoriously heavy-weight~\cite{carns:ipdps09-pvfs,
eshel:fast10-panache}. The number of files or size of the files is indicative
of the progress. This practice is not too different from cloud systems that use the
file system to manage the progress of jobs; Spark/Hadoop writes to temporary
files, renames them when complete, and creates a ``DONE" file to indicate to
the runtime that the task did not fail and should not be re-scheduled on
another node. \newcomment{Also, the browser interface lets Hadoop/Spark users check
progress by querying the file system and returning a \% of job complete
metric.}

@@

As expected, syncing namespace updates too frequently has the highest overhead
(up to 9\% overhead if done every second). The optimal sync interval for
performance is 10 seconds, which only incurs 2\% overhead, because larger
intervals must write more updates to disk and network. For the 25 second
interval, the client only pauses 3-4 times but each sync writes about 278
thousand updates at once, which is a journal of size 678MB.

### 2018-01-08 paper/sections/7_conclusion.tex
paper: typos
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

Relaxing consistency/durability semantics in file systems is a double-edged
sword. While it performs and scales better, it alienates applications that rely
on strong consistency and durability.  Cudele lets
\oldcomment{users}\newcomment{administrators} assign consistency/durability
guarantees to subtrees in the global namespace, resulting in 
custom fit semantics for application. We show how applications can co-exist and
perform well in a global namespace and our prototype enables studies that
adjust these semantics over {\it time and space}, where subtrees can change
without ever moving the data they reference.

%This approach is superior to mounting different storage systems in a global
%namespace because there is no need to provision dedicated storage clusters to
%applications or move data between these systems.  
Cudele prompts many avenues for future work.  First is to co-locate HPC
workflows with real highly parallel runtimes from the cloud in the same
namespace. This setup shows how Cudele reasonably incorporates both programming
models (client-driven parallelism and user-defined workflows) at the same time
and should show large performance gains.  Second is dynamically changing
semantics of a subtree from stronger to weaker guarantees (or vice versa).  For
example, the results of a Hadoop job do not need to be migrated into CephFS for
other processing; instead the \oldcomment{user}\newcomment{administrator} can
change the semantics of the HDFS subtree into a CephFS subtree, which may cause
metadata/data movement to ensure strong consistency. Third is embeddable
policies, where child subtrees have specialized features but still maintain
guarantees of their parent subtrees.  For example, a RAMDisk subtree is POSIX
IO-compliant but relaxes durability constraints, so it can reside under a POSIX
IO subtree that is strongly consistent.

>>>>

Relaxing consistency/durability semantics in file systems is a double-edged
sword. While the technique performs and scales better, it alienates applications that rely
on strong consistency and durability.  Cudele lets
\oldcomment{users}\newcomment{administrators} assign consistency/durability
guarantees to subtrees in the global namespace, resulting in 
custom fit semantics for applications. We show how applications can co-exist and
perform well in a global namespace and our prototype enables studies that
adjust these semantics over {\it time and space}, where subtrees can change
without ever moving the data they reference.

%This approach is superior to mounting different storage systems in a global
%namespace because there is no need to provision dedicated storage clusters to
%applications or move data between these systems.  
Cudele prompts many avenues for future work.  First is to co-locate HPC
workflows with real highly parallel runtimes from the cloud in the same
namespace. This setup shows how Cudele reasonably incorporates both programming
models (client-driven parallelism and user-defined workflows) at the same time
and should show large performance gains.  Second is dynamically changing
semantics of a subtree from stronger to weaker guarantees (or vice versa). This
reduces data movement across storage cluster and file system boundaries so
the results of a Hadoop job do not need to be migrated into CephFS for
other processing; instead the \oldcomment{user}\newcomment{administrator} can
change the semantics of the HDFS subtree into a CephFS subtree, which may cause
metadata/data movement to ensure strong consistency. Third is embeddable
policies, where child subtrees have specialized features but still maintain
guarantees of their parent subtrees.  For example, a RAMDisk subtree is POSIX
IO-compliant but relaxes durability constraints, so it can reside under a POSIX
IO subtree alongside a globally durable subtree.
